### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
update CAFS report

There is a difference in the amount of direct impact from the suppression agent at the three spatial locations. Therefore, the maximum temperature differences for each thermocouple on the three different arrays should also be analyzed separately. Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively. Note that for thermocouple array A3, which has the least amount of direct suppression, the least squared error line is closest to the uniform impact line (black solid line) meaning that within the experimental uncertainty, water and CAFS are indistinguishable. Thermocouple array A3 also has the strongest statistical fit compared to arrays A1 and A2.

@@

>>>>

There is a difference in the amount of direct impact from the suppression agent at the three spatial locations. Therefore, the maximum temperature differences for each thermocouple on each of the three arrays should also be analyzed separately. Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively. Note that thermocouple array A3, the array which has the least amount of direct suppression, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents. The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAFS and water are indistinguishable. Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAFS.

@@

The thermocouple array data can also also be decomposed as a function of nozzle position: 12 middle position replicates and 3 back position replicates. Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 12 replicate tests with the monitor nozzle in the middle position. Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 3 replicate tests with the monitor nozzle in the back position.
